Fig2

### 2020-02-21 analysis/figure-2.Rmd
better bar graphs, no facets

makenewbargraph <- function(whichtissue, myxlab, whichcomparison, lowlim, higherlim){
  p <- allDEG2 %>%
    filter(tissue == whichtissue,
           comparison == whichcomparison) %>%
  ggplot(aes(x = comparison,  fill = direction)) +
    geom_bar(position = "dodge") +
    facet_grid(tissue~sex) +
    theme_B3() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none")  +
    guides(fill = guide_legend(nrow = 1)) +
    labs(x = myxlab, 
         y = "Total DEGs") +
  geom_text(stat='count', aes(label=..count..), vjust =-0.5, 
           position = position_dodge(width = 1),
           size = 2.5, color = "black")  + 
      ylim(lowlim, higherlim)
  return(p)
}

@@

b <- makenewbargraph(tissuelevel, "External stimuli", "eggs vs. chicks", 0, 1250)  + theme(strip.text.y = element_blank()) +
  scale_fill_manual(values = c("#80cdc1", "#018571"))
c <- makenewbargraph(tissuelevel, "Pituitary PRL expression   ", "lo vs. hi PRL   ", 0, 1250) + labs(y = NULL) + theme(axis.text.y = element_blank()) +
  scale_fill_manual(values = c("#dfc27d", "#a6611a"))

plot_grid(b, c, rel_widths = c(1,1), nrow = 1, labels = "auto", label_size = 12)
```

>>>>

@@

```{r fig2b, fig.width=5, fig.height=5}

makenewbargraph <- function(whichtissue, whichsex,  whichcomparison, lowlim, higherlim){
  p <- allDEG2 %>%
    filter(tissue == whichtissue,
           comparison == whichcomparison,
           sex == whichsex) %>%
    ggplot(aes(x = comparison,  fill = direction)) +
    geom_bar(position = "dodge", drop = FALSE) +
    theme_B3() +
    theme(legend.position = "none")  +
    guides(fill = guide_legend(nrow = 1)) +
    labs( y = whichtissue) +
  geom_text(stat='count', aes(label=..count..), vjust =-0.5, 
           position = position_dodge(width = 1),
           size = 2.5, color = "black")  + 
      ylim(lowlim, higherlim) +
  scale_fill_manual(values = allcolors, name = "higher in")   + 
    theme(axis.text.x = element_blank()) 
  return(p)
}

b11 <- makenewbargraph("hypothalamus", "female","eggs vs. chicks", 0, 800) +  labs(subtitle = "females", x = NULL, y = "Hyp. DEGS")
b21 <- makenewbargraph("pituitary", "female","eggs vs. chicks", 0, 800)  + labs(x = NULL, y = "Pit. DEGS")
b31 <- makenewbargraph("gonad", "female", "eggs vs. chicks", 0, 800) + labs(x = "eggs vs. chicks", y = "Gon. DEGS")   
b112131 <- plot_grid(b11,b21,b31, nrow = 3, rel_heights = c(1.1,1,1.1))

b12 <- makenewbargraph("hypothalamus", "male",  "eggs vs. chicks", 0, 800) + labs(subtitle = "males", x = NULL)+ 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())
b22 <- makenewbargraph("pituitary", "male", "eggs vs. chicks", 0, 800) + labs(x = NULL)+ 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())
b32 <- makenewbargraph("gonad", "male", "eggs vs. chicks", 0, 800) + labs(x = "eggs vs. chicks")   + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())
b122232 <- plot_grid(b12, b22,b32, nrow = 3, rel_heights = c(1.1,1,1.1))

c11 <- makenewbargraph("hypothalamus", "female", "lo vs. hi PRL   ", 0, 2500) +  labs(subtitle = "females", x = NULL) + 
  theme(axis.title.y = element_blank())
c21 <- makenewbargraph("pituitary", "female", "lo vs. hi PRL   ", 0, 2500)  + labs(x = NULL)+ 
  theme(axis.title.y = element_blank())
c31 <- makenewbargraph("gonad", "female", "lo vs. hi PRL   ", 0, 2500) + labs(x = "lo vs. hi PRL")  + 
  theme(axis.title.y = element_blank()) 
c112131 <- plot_grid(c11,c21,c31, nrow = 3, rel_heights = c(1.1,1,1.1))

c12 <- makenewbargraph("hypothalamus", "male",  "lo vs. hi PRL   ", 0, 2500) + labs(subtitle = "males", x = NULL)+ 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())
c22 <- makenewbargraph("pituitary", "male", "lo vs. hi PRL   ", 0, 2500) + labs(x = NULL)+ 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())
c32 <- makenewbargraph("gonad", "male", "lo vs. hi PRL   ", 0, 2500) + labs(x = "lo vs. hi PRL")   + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())
c122232 <- plot_grid(c12, c22,c32, nrow = 3, rel_heights = c(1.1,1,1.1))

hypothesisbars <-  plot_grid(b112131, b122232, c112131, c122232, nrow = 1, rel_widths = c(1.3, 1, 1.1, 1),
          labels = c("b", " ", "c", " "), label_size = 12)

expdesign2 <- png::readPNG("../figures/images/DoveParentsRNAseq_hypothesis.png")
expdesign2 <- ggdraw() +  draw_image(expdesign2, scale = 1)

plot_grid(expdesign2, hypothesisbars, rel_heights = c(0.5,1), nrow = 2, labels = c("a", " "), label_size = 12)
```

```{r GO}
## shinygo termshttp://bioinformatics.sdstate.edu/go/
allDEG2 %>% filter(tissue == "pituitary", direction == "chicks") %>% arrange(gene) %>% pull(gene) # nervous systme development, neurogenesis, neuron differentiaion 
allDEG2 %>% filter(tissue == "pituitary", direction == "eggs") %>% arrange(gene) %>% pull(gene) # miotic cell cycle, cell cycle, cell cycle process
allDEG2 %>% filter(tissue == "pituitary", direction == "hi") %>% arrange(gene) %>% pull(gene) # this 1000 combined with next 10000
allDEG2 %>% filter(tissue == "pituitary", direction == "hi") %>% arrange(desc(gene)) %>% pull(gene) # Cellular localization, #Cellular protein localization, Protein targeting to ER

#miotic cell cycle, miotic cell cycle process, cell cycle
allDEG2 %>% filter(tissue == "pituitary", direction == "lo") %>% arrange(gene)  %>% pull(gene)   # this 1000 combined with next 10000
allDEG2 %>% filter(tissue == "pituitary", direction == "lo") %>% arrange(desc(gene)) %>% pull(gene) #Anatomical structure morphogenesis, Regulation of developmental process, Regulation of signaling

allDEG2 %>%
  filter(tissue == "pituitary") %>%
  select(sex, tissue, comparison, gene) %>%
  group_by(sex, tissue, gene) %>%
  summarize(groups = str_c(comparison , collapse = " "))   %>%
   group_by(sex, tissue, groups) %>%
  summarize(n = n()) %>%
  arrange(desc(n))

allDEG2 %>%
  filter(tissue == "pituitary") %>%
  select(sex, tissue, comparison, gene) %>%
  group_by(sex, tissue, gene) %>%
  summarize(groups = str_c(comparison , collapse = " "))  %>%
  filter(groups == "eggs vs. chicks") %>%
  arrange(gene) %>%
  distinct(gene) %>%
  pull(gene)  # Nervous system development, Cell development, Anatomical structure morphogenesis

allDEG2 %>%
  filter(comparison == "eggs vs. chicks") %>%
  group_by(sex, tissue, comparison, direction) %>%
  summarize(n = n()) %>%
  arrange(comparison, direction, tissue, sex)

allDEG2 %>%
  filter(comparison == "lo vs. hi PRL   ") %>%
  group_by(sex, tissue, comparison, direction) %>%
  summarize(n = n()) %>%
  arrange(comparison, direction, tissue, sex)

```
```{r}
allDEG2 %>%
  filter(tissue == "pituitary") %>%
  select(sex, tissue, comparison, gene) %>%
  group_by(sex, tissue, gene) %>%
  summarize(groups = str_c(comparison , collapse = " "))  %>%
  filter(groups == "lo vs. hi PRL   ") %>%
  arrange(gene) %>%
  distinct(gene) %>%
  pull(gene)  # Nervous system development, Cell development, Anatomical structure morphogenesis

allDEG2 %>%
  group_by(sex, tissue, comparison, direction) %>%
  summarize(n = n())
```
